Liveness-Based Garbage Collection for Lazy Languages

### 2016-04-18 paper/paper.tex
Added reference to TIM

In  this work  we show  that  static analysis  of heap  data can  help
garbage  collectors   in  reclaiming   more  garbage.    The  specific
contributions of this paper are:
\added{
\begin{itemize}
\item {\color{Myblue}We  propose an interprocedural liveness  based GC
  scheme  for a  lazy first  order functional  language and  prove its
  correctness.  To the  best of our knowledge, this is  the first work
  that uses  the results  of an  interprocedural liveness  analysis to
  garbage    collect    both     evaluated    data    and    closures.
  Thomas~\cite{Thomas19951} describes a  copying garbage collector for
  the  Three  Instruction  Machine  (TIM)  that  only  preserves  live
  closures in a function's environment (also called a frame). However,
  in the absence of  details, it is not clear whether  a) the scope of
  the method is interprocedural, and b) it handles algebraic datatypes
  like lists (the original design of TIM did not).  All other previous
  attempts~\cite{shaham01heap,  ran.shaham-sas03,  shaham02estimating,
    asati14lgc, karkare06effectiveness} involved  either imperative or
  eager functional languages.}
%% The novelty of our approach is in handling of
%%   liveness  of closures,  an  issue  that arises  due  to laziness  at
%%   runtime.}

>>>>

In  this work  we show  that  static analysis  of heap  data can  help
garbage  collectors   in  reclaiming   more  garbage.    The  specific
contributions of this paper are:
\added{
\begin{itemize}
\item {\color{Myblue}We  propose an interprocedural liveness  based GC
  scheme  for a  lazy first  order functional  language and  prove its
  correctness.  To the  best of our knowledge, this is  the first work
  that uses  the results  of an  interprocedural liveness  analysis to
  garbage    collect    both     evaluated    data    and    closures.
  Thomas~\cite{Thomas19951} describes a  copying garbage collector for
  the Three  Instruction Machine (TIM)~\cite{Fairbairn1987}  that only
  preserves live closures  in a function's environment  (also called a
  frame). However, in the absence of  details, it is not clear whether
  a) the  scope of the  method is  interprocedural, and b)  it handles
  algebraic datatypes like lists (the original design of TIM did not).
  All  other  previous attempts~\cite{shaham01heap,  ran.shaham-sas03,
    shaham02estimating,  asati14lgc, karkare06effectiveness}  involved
  either imperative or eager functional languages.}
%% The novelty of our approach is in handling of
%%   liveness  of closures,  an  issue  that arises  due  to laziness  at
%%   runtime.}
